Gibbon Analysis

### 2018-10-31 BatangToru/Gibbon Analysis.Rmd
old changes?

# Looking at the data:
```{r}
library('DEVDEV5') # load the development version of the LT2D package
Data = read.csv('GibbonSiamang.csv',header=T) # load the x and y data
Data = subset(Data, Data$Species == 1)
x = Data$PP.Distance ; y = Data$Forward.Distance
```

>>>>

# Looking at the data:
```{r}
library('LT2D') # load the development version of the LT2D package
Data = read.csv('GibbonSiamang.csv',header=T) # load the x and y data
Data = subset(Data, Data$Species == 1)
x = Data$PP.Distance ; y = Data$Forward.Distance
```
